
\twocolumn[{%
\begin{center}
  {\LARGE \textbf{\textsf{Top Quark Seminar 10}}} \\
  \vspace{1em}
  {\Large \textbf{\textsf{Igor Babuschkin}}} \\
  \vspace{1em}
  {\large \textbf{\textsf{6th January 2015}}}
  \section*{Summary of \enquote{Search for pair and single production of new heavy quarks that decay to a $Z$ boson and a third-generation quark in $pp$ collisions at $\sqrt{s}=\SI{8}{TeV}$ with the ATLAS detector}}
\end{center}
}]

The paper\cite{atlas} is a recent analysis exploring an ATLAS dataset taken during 2012 (with $\SI{20}{fb}^{-1}$) for the presence of new, vector-like heavy quarks.
Such new quarks can have a top-like charge (they are then referred to as $T$) or a bottom-like charge ($B$).
The analysis specifically looks for the decay modes $T\to Zt$ and $B\to Zb$.
Both pair and single production of $T$ and $B$ are investigated.

The search for vector-like quarks can be motivated by the fact that they often arise in non-supersymmetric models solving the  naturalness problem\cite{berger}.

When preparing the dataset for the analysis, the presence of a $Z$ boson is inferred from the event by combining a pair of muons or electrons with opposite charges and checking if their invariant mass is within \SI{10}{GeV} of the known $Z$ mass.

In addition, the $t$ and $b$ quarks need to be considered:
While the presence of a $b$ quark can be detected via a $b$-jet, the decaying top quark can produce further leptons (the trilepton case) and further $b$-jets.
The dataset contains roughly $10^6$ dilepton and $10^3$ trilepton events after reconstruction and preselection.

Both signal and background events are simulated using a variety of Monte Carlo generators.
Important background final states that needed to be modeled were $Z + $jets and $Z + q\overline{q} +$ jets, as well as $WZ$, $ZZ$, $WW$ for the trilepton case.
To derive a theoretical prediction for the $T$ and $B$ cross sections, an NNLO calculation was employed.
The simulated signal samples (for various masses of the vector-like quark) are generated using a leading order generator and normalized using the NNLO calculation.

A variable that is important for selecting signal events is the $Z$ boson transverse momentum, which would tend to be higher in actual vector-like quark decays.
The final discriminating variable is $m(Zb)$ in the dilepton case and $H_\text{T}(\text{jets}+\text{leptons})$ for the trilepton case.

After applying the selection, the number of signal candidates is reduced greatly and is of the order or one order above the number of expected $T$ or $B$ events.
It is compatible with the Standard Model expectation in all decay channels.

The authors conclude that no sufficient evidence for different models of $T$ and $B$ could be observed.
Lower limits on the masses of $T$ and $B$ (depending on the respective model) could be set at around \SI{700}{GeV} using the $\text{CL}_\text{s}$ method.
